Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
Scenario polished

The victim in these scenarios is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to vulnerable.com, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
The attacker.com website embeds the polyglot content from vulnerable.com, but
coerces the browser to interpret it as the malicious content type. 
The capabilities of the malicious format determine the 
severity of the consequences of exploitation.

>>>>

The scenario, illustrated in Figure~\ref{fig:scenario}, describe how the attack proceed, from the infiltration of the origin, to the compromise of the victim.
The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to vulnerable.com, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
The attacker.com website embeds the polyglot content from vulnerable.com, but
coerces the browser to interpret it as the malicious content type. 
The capabilities of the malicious format determine the 
severity of the consequences of exploitation.
